### 2019-03-06 gammSlice.Rmd
init

---
title: "gammSlice 用法"
author: "Jin"
date: "2019-03"
output:
  bookdown::html_document2:
    number_sections: true
    seq_numbering: true
    fig_caption: true
    highlight: haddock
    theme: null
    md_extensions: +east_asian_line_breaks
    keep_md: true
    toc: false
    pandoc_args: ["--filter", "pandoc-crossref", "-M", "eqnPrefix="]
  bookdown::word_document2:
    fig_caption: true
    reference_docx: ./style/word-styles-02.docx
    md_extensions: +east_asian_line_breaks
    pandoc_args: ["--filter", "pandoc-crossref"]
  bookdown::pdf_document2:
    keep_tex: yes
    toc: false
    latex_engine: xelatex
    md_extensions: +east_asian_line_breaks
    pandoc_args: ["--listing", "--filter", "pandoc-crossref"]
css: ./style/markdown.css
autoEqnLabels: true
eqnPrefixTemplate: ($$i$$)
linkReferences: true
bibliography: Bibfile.bib
csl: ./style/chinese-gb7714-2005-numeric.csl
link-citations: true
---

**TODO**

```{r setup, echo=F}
knitr::opts_knit$set(root.dir = getwd())
knitr::opts_chunk$set(echo = FALSE, results = 'hide')
knitr::opts_chunk$set(warning = FALSE, message=FALSE)
```

```{r prepare}
rm(list=ls())
options(digits=4)
options(scipen=100)
graphics.off()
Sys.setlocale("LC_ALL", "Chinese")
```

# 简介

# 参考文献
[//]: # (\bibliography{Bibfile})