### 2019-06-02 report/07-conclusion.Rmd
init report

---
title: "开题报告"
author: "Li"
date: "2019-04-15"
css: ./style/markdown.css
autoEqnLabels: true
eqnPrefixTemplate: ($$i$$)
linkReferences: true
bibliography: Bibfile.bib
notice: '@*'
csl: ./style/chinese-gb7714-2005-numeric.csl
link-citations: true
---

**TODO**

```{r setup, echo=F}
knitr::opts_knit$set(root.dir = getwd())
knitr::opts_chunk$set(echo = FALSE, results = 'hide')
knitr::opts_chunk$set(warning = FALSE, message=FALSE)
```

```{r prepare}
rm(list=ls())
options(digits=4)
options(scipen=100)
graphics.off()
Sys.setlocale("LC_ALL", "Chinese")
```

# 模型设定

# 参考文献 {-}
[//]: # (\bibliography{Bibfile})